\Large \bf Uncovering Bugs in Distributed Storage Systems\\during Testing (not in Production!)

### 2015-12-25 evaluation.tex
major update to address PC and shepherd comments

\newcommand{\colspacing}{\hspace{1.8em}}
\begin{table}[t]
\small
\centering
\setlength{\tabcolsep}{0.3em}
\begin{tabular}{l rrrrr rr}
\centering
\input{experiments/tables/statistics.tex}
\end{tabular}
\caption{Statistics from modeling the environment of the three \Microsoft MyCloud-based systems under test. The ($\star$) denotes ``awaiting confirmation''.}
\label{tab:stats}
%\vspace{-3mm}
\end{table}

@@

Modeling the environment of the Extent Manager in the \Azure Storage vNext system required approximately two person weeks of part-time developing. The \psharp test harness for this system is the smallest (in lines of code) from the three case studies. This was because this modeling exercise aimed to reproduce the particular liveness bug that was haunting the developers of vNext.

Developing both the MigratingTable system and its \psharp test harness took approximately five person weeks. The \psharp test harness was developed in parallel with the actual system. This is in contrast with the other two case studies discussed in this paper, where the modeling activity occurred independently and after the development process had finished.

@@

Using \psharp we managed to uncover 8 serious bugs in our case studies. As discussed earlier in the paper, these bugs were hard to find with traditional testing techniques, but \psharp managed to uncover them and reproduce them in a small setting. According to the developers, the traces of \psharp were useful, as it allowed them to understand the source of the bug and fix it in a timely manner. After the developers fixed all the discovered bugs, we optionally reintroduced them one-by-one to evaluate the effectiveness of different \psharp systematic testing strategies in finding these bugs.

Table~\ref{tab:testing} presents the results from running the \psharp systematic testing engine on each case study with a re-introduced bug using the random and PCT schedulers. We chose to use controlled random scheduling, because it has proven to be efficient for finding concurrency bugs~\cite{thomson2014sct, deligiannis2015psharp}. The CS column shows which case study corresponds to each bug: ``1'' is for the \Azure Storage vNext; and ``2'' is for MigratingTable. We do not include the Fabric case study, as we are awaiting confirmation of the found bug (see \S\ref{sec:cases:fabric}).

@@

For the vNext case study, the random scheduler was able to reproduce the ExtentNodeLivenessViolation bug in less than 10 seconds. The reason that the number of scheduling steps to find the bug is much higher than the rest of the bugs in the table is that this bug is a liveness violation: as discussed in \S\ref{sec:overview:testing} we leave the program to run for a long time before checking if the liveness property holds. The PCT scheduler was unable to find the bug using the bug depth of 2, which suggests that the bug requires a larger depth bound to be found.

For the MigratingTable case study, we evaluated the \psharp test harness of \S\ref{sec:cases:migration} on eleven buggy versions of the system, including eight \emph{organic} bugs that actually occurred in development and three \emph{notional} bugs (denoted by $*$), which are other code changes that we deemed interesting ways of making the system incorrect. The test found seven of the organic bugs, which are listed first in Table~\ref{tab:testing}. The remaining four bugs (denoted by $\diamond$) were not caught with our default test harness in the 100,000 executions (a process that required less than 30 minutes). We believe this is because the inputs and schedules that trigger them are too rare in our distribution. To confirm this, we wrote a custom test case for each bug with a specific input that triggers it and were able to quickly reproduce the bugs, as shown. This method is useful for regression testing, but one could not use it during development with no prior knowledge about the bugs.

>>>>

\newcommand{\colspacing}{\hspace{1.8em}}
\begin{table}[t]
\small
\centering
\setlength{\tabcolsep}{0.3em}
\begin{tabular}{l rrrrr rr}
\centering
\input{experiments/tables/statistics.tex}
\end{tabular}
\caption{Statistics from modeling the environment of the three Microsoft MyCloud-based systems under test. The ($\star$) denotes ``awaiting confirmation''.}
\label{tab:stats}
\vspace{-3mm}
\end{table}

@@

Modeling the environment of the Extent Manager in the Azure Storage vNext system required approximately two person weeks of part-time developing. The \psharp test harness for this system is the smallest (in lines of code) from the three case studies. This was because this modeling exercise aimed to reproduce the particular liveness bug that was haunting the developers of vNext.

Developing both MigratingTable and its \psharp test harness took approximately five person weeks. The harness was developed in parallel with the actual system. This differs from the other two case studies, where the modeling activity occurred independently and after the development process had finished.

@@

Using \psharp we managed to uncover 8 serious bugs in our case studies. As discussed earlier in the paper, these bugs were hard to find with traditional testing techniques, but \psharp managed to uncover them and reproduce them in a small setting. According to the developers, the traces of \psharp were useful, as it allowed them to understand the source of the bug and fix it in a timely manner. After the developers fixed all the discovered bugs, we optionally reintroduced them one-by-one to evaluate the effectiveness of different testing strategies.

Table~\ref{tab:testing} presents the results from running the \psharp systematic testing engine on each case study with a re-introduced bug using the random and PCT schedulers. We chose to use controlled random scheduling, because it has proven to be efficient for finding concurrency bugs~\cite{thomson2014sct, deligiannis2015psharp}. The CS column shows which case study corresponds to each bug: ``1'' is for the Azure Storage vNext; and ``2'' is for MigratingTable. We do not include the Fabric case study, as we are awaiting confirmation of the found bug (see \S\ref{sec:fabric}).

We have implemented two different schedulers that are responsible for making scheduling and other non-deterministic choices: a \emph{random} scheduler that makes each nondeterministic choice randomly, and a \emph{probabilistic concurrency testing}~\cite{burckhardt2010pct} (PCT) scheduler. It is straightforward to create a new scheduler by implementing the \texttt{ISchedulingStrategy} interface~\cite{desai2015systematic} exposed by the \psharp libraries. The interface exposes callbacks that are invoked by the \psharp testing engine for taking decisions regarding which machine to schedule next, and can be used for developing both generic and application-specific schedulers.

@@

For the vNext case study, the random scheduler was able to reproduce the ExtentNodeLivenessViolation bug in less than 10 seconds. The reason that the number of scheduling steps to find the bug is much higher than the rest of the bugs in the table is that this bug is a liveness violation: as discussed in \S\ref{sec:overview:liveness} we leave the program to run for a long time before checking if the liveness property holds. The PCT scheduler was unable to find the bug using the bug depth of 2, which suggests that the bug requires a larger depth bound to be found.

For the MigratingTable case study, we evaluated the \psharp test harness of \S\ref{sec:migrating} on eleven buggy versions of the system, including eight \emph{organic} bugs that actually occurred in development and three \emph{notional} bugs (denoted by $*$), which are other code changes that we deemed interesting ways of making the system incorrect. The test found seven of the organic bugs, which are listed first in Table~\ref{tab:testing}. The remaining four bugs (denoted by $\diamond$) were not caught with our default test harness in the 100,000 executions (a process that required less than 30 minutes). We believe this is because the inputs and schedules that trigger them are too rare in our distribution. To confirm this, we wrote a custom test case for each bug with a specific input that triggers it and were able to quickly reproduce the bugs, as shown. This method is useful for regression testing, but one could not use it during development with no prior knowledge about the bugs.

### 2015-12-25 intro.tex
major update to address PC and shepherd comments

We have found that checking high-level specifications is necessary but not sufficient, due to the gap between the specification and the executable code. Our goal is to bridge this gap. We propose a new methodology that validates high-level specifications directly on the executable code. Our methodology is different from prior approaches that required developers to either switch to an unfamiliar domain specific language~\cite{killian2007life, desai2015building}, or manually annotate and instrument their code~\cite{simsa2011dbug}. Instead, we allow developers to test \emph{production code} by writing test harnesses in \csharp, a mainstream programming language. This significantly lowered the acceptance barrier for adoption by the Microsoft Azure team.

%We present a new method for testing an implementation of a distributed system and uncovering bugs before the system is released in the wild.
Our methodology is based on \psharp~\cite{deligiannis2015psharp}, an extension of \csharp that provides support for modeling, specification, and systematic testing of distributed systems written in Microsoft's .NET framework. To test a distributed system with \psharp, the programmer augments the original system code with three artifacts -- a model of the nondeterministic execution environment of the system, a concurrent test harness that drives the system towards interesting behaviors, and safety or liveness specifications.
The \psharp testing engine then systematically explores all behaviors exercised by the test harness and validates them against the provided specifications.

We have applied \psharp to three distributed storage systems inside Microsoft: Azure Storage vNext; Azure Table Live Migration; and Azure Service Fabric.
%a distributed storage system; a system for migrating data across partitions; and a big-data computing system.
We uncovered numerous bugs in these systems, including, most notably, a subtle liveness bug that only intermittently manifested during stress testing for months without being fixed.
Our testing approach uncovered this bug in a very small setting, which made it easy for developers to examine traces, identify, and fix the problem.
%Our experience demonstrates that bugs in production do not need a large setting to be reproduced; they can be reproduced in small settings with easy to understand traces.

To summarize, our contributions are as follows:
\begin{itemize}
\item We present a new methodology that allows flexible modeling of the environment of a distributed system using simple language mechanisms in \psharp.
\item Because \psharp is an extension of \csharp, our infrastructure can test production code written in \csharp.
\item We present three case studies of using \psharp to test production distributed systems, finding bugs that could not be found with traditional testing techniques.
\item We show that \psharp can reproduce bugs in production-scale distributed systems in a small setting with easy to understand traces.
\end{itemize}

>>>>

We have found that checking high-level specifications is necessary but not sufficient, due to the gap between the specification and the executable code. Our goal is to bridge this gap. We propose a new methodology that validates high-level specifications directly on the executable code. Our methodology is different from prior approaches that required developers to either switch to an unfamiliar domain specific language~\cite{killian2007life, desai2015building}, or manually annotate and instrument their code~\cite{simsa2011dbug}. Instead, we allow developers to systematically test \emph{production code} by writing test harnesses in \csharp, a mainstream programming language. This significantly lowered the acceptance barrier for adoption by the Microsoft Azure team.

Our testing methodology is based on \psharp~\cite{deligiannis2015psharp}, an extension of \csharp that provides support for modeling, specification, and systematic testing of distributed systems written in the Microsoft .NET framework. To use \psharp for testing, the programmer has to augment the original system with three artifacts: a model of the nondeterministic execution environment of the system; a test harness that drives the system towards interesting behaviors; and safety or liveness specifications. \psharp then systematically exercises the test harness and validates program behaviours against the provided specifications.

The original \psharp paper~\cite{deligiannis2015psharp} discussed language design issues and data race detection for programs written in \psharp, whereas this work focuses on using \psharp to test three distributed storage systems inside Microsoft: Azure Storage vNext; Live Table Migration; and Azure Service Fabric. We uncovered numerous bugs in these systems, including a subtle liveness bug that only intermittently manifested during stress testing for months without being fixed. Our testing approach uncovered this bug in a very small setting, which made it easy for developers to examine traces, identify, and fix the problem.

To summarize, our contributions are as follows:
\begin{itemize}
\item We present a new methodology for modeling, specifying properties of correctness, and systematically testing real distributed systems with \psharp.
\item We discuss our experience of using \psharp to test three distributed storage systems that are used inside Microsoft, finding subtle bugs that could not be found with traditional testing techniques.
\item We evaluate the cost and benefits of using our approach, and show that \psharp can detect bugs in a small setting and with easy to understand traces.
\end{itemize}

### 2015-12-25 migrating.tex
major update to address PC and shepherd comments

The modeling and testing approach described in the earlier sections of the paper is not specific to the vNext system. \psharp is a generic framework for .NET distributed systems. We showcase this capability by presenting developer experience of using \psharp to model and test two other systems used in production inside \Microsoft.

\subsection{Live \Azure Table Migration}
\label{sec:cases:migration}

Live \Azure Table Migration (MigratingTable) is a library designed to \emph{transparently} migrate a data set between tables in an \Azure Storage service \emph{while} an application is accessing this data set. This case study is particularly interesting because MigratingTable was \emph{co-developed} with its \psharp test harness. This co-development process resulted in the discovery of several tricky bugs before the system went into production (see \S\ref{sec:eval}). The MigratingTable testing effort differs from the vNext case study: the vNext developers focused on a single liveness property, while the MigratingTable test harness checks complete compliance with an interface (safety) specification.

MigratingTable provides a \emph{virtual table} that has an interface similar to an ordinary \Azure table. This interface is named \texttt{IChainTable}. A virtual table is backed by a pair of \emph{old} and \emph{new} \emph{backend} tables, both of which implement \texttt{IChainTable}. A \emph{migrator} job is responsible for moving all data from the old table to the new table in the background. Meanwhile, each read and write operation issued to the virtual table is translated to a sequence of reads and writes on the backend tables according to a protocol, which intends to guarantee that when multiple applications issue \emph{input} operations to virtual tables that are backed by the same backend tables, the output is compliant with the specification of \texttt{IChainTable} for the combined \emph{input history} as if all the operations were done on a single table. The goal of using \psharp was to systematically test this property.

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{img/mocked_migration}
\caption{The \psharp test harness of MigratingTable (each box with a dotted line represents one \psharp machine).}
\label{fig:mockedmigration}
\end{figure}

@@

\PTComment{This para is slightly unclear.} The developers instrumented MigratingTable to report the intended \emph{linearization point} of each input operation on its corresponding virtual table. This allows the \psharp test harness to keep \texttt{SpecTable} in sync with the virtual table: the \texttt{Service} machine sends each input operation to \texttt{SpecTable} when the linearization point on the virtual table is reached. The output of the operation on the virtual table is then checked against its output on \texttt{SpecTable}.

@@

\psharp captures and controls all the interleaving in the system, and systematically explores them. To ensure that \texttt{SpecTable} is never observed to be out of sync with the backend tables, which could lead to false positives, after the \texttt{Tables} machine processes a backend operation, it enters a state that defers further backend operations until MigratingTable has reported whether the backend operation was a linearization point and (if so) \PTComment{I don't quite get this. Could you case-split here on whether the operation was or was not a linearization point?} the operation on \texttt{SpecTable} has been completed.

@@

\subsection{\Azure Service Fabric}
\label{sec:cases:fabric}

\Azure Service Fabric
%\footnote{\url{azure.microsoft.com/campaigns/service-fabric/}}
(or Fabric for short) is a platform and API for creating reliable services that execute on a cluster of machines. 
%The developer writes a service that receives requests (e.g.\ from some client program via HTTP requests) and mutates its state based on these requests. 
In order to make the user-written service \emph{reliable}, Fabric launches several \emph{replicas} (copies) of the service, where each replica runs as a separate process on a different node in the cluster.
%\PTComment{Cut: description of primary and secondaries, and electing a new primary.}
One replica is selected to be the \emph{primary} which serves client requests; the rest are \emph{secondaries}. The primary replicates state changes to the secondaries 
%by sending them \emph{replication requests}.
so that all replicas eventually have the same state. 
If the primary fails,
% (e.g.\ if the node on which the primary is running crashes), 
Fabric elects one of the secondaries to be the new primary and launches another secondary; the new secondary will receive 
%a full or partial copy (depending on whether persistent storage is used) 
a copy
of the state of the new primary in order to ``catch up'' with the other secondaries. 
%Fabric provides a name-resolution service so that clients can always find the current primary.
%The state of the service is replicated from the \emph{primary} replica to the other \emph{secondary} replicas for redundancy.
User-written Fabric services are complex asynchronous and distributed applications, and are thus challenging to test.
% They are interesting targets for systematic testing with \psharp{}.

Our primary goal was to create a \psharp{} model of Fabric to allow
thorough testing of services, where Fabric's asynchrony is controlled 
by the \psharp{} runtime.
The model is written once
to include all behaviours of Fabric, including simulating failures and recovery,
so that it can be reused repeatedly to test multiple Fabric services.
This was the largest modeling exercise among the case studies but the cost
was amortized across testing multiple servies. This is analogous to the work
on driver verification \cite{ball2011slam} where the cost of developing a model
of the Windows kernel was amortized across testing multiple device drivers.
Note that we model the lowest Fabric API layer (\texttt{Fabric.dll})
which is currently not documented for use externally.
We target internally-developed services that invoke the lowest layer.

\psharp's systematic testing was very helpful in debugging the model itself.
% Without systematic testing, we feel even catching bugs in the model 
% would have been difficult.
In order to perform systematic testing on our model,
we wrote a simple service in \psharp{}
that runs on our Fabric model.
%made up of a single machine
% and executed it on the Fabric model,
% thus yielding a pure \psharp{} system.
We tested a scenario where the primary replica
fails at some non-deterministic point
within the execution.
One such bug that we found
involved
the primary replica
failing
when a secondary replica
was about to receive a copy of the state;
the secondary was then elected to be the new primary
and yet, because the secondary stopped waiting for
a copy of the state, it was
also promoted to be an \emph{active} secondary
(one that has caught up with the other secondaries).
This caused an assertion failure in our model
allowing us to detect and fix this incorrect behaviour.

%\PTComment{Cut: prior work created a Fabric model\ldots}
% Prior work~\cite{deligiannis2015psharp}
% created a model of Fabric with limited functionality;
% it used a mixture of \csharp{} and \psharp{} internally,
% only supported one in-flight replication request
% (which restricts the asynchrony that can be tested),
% and only supported one Fabric service.
% Our new Fabric model was re-written to use only \psharp{}
% internally,
% support an arbitrary number of Fabric services and in-flight replication requests,
% and in general be a more complete model of Fabric.
% Note that \csharp{} code is still required to interface with the existing
% \csharp{} service code.
% We refer to our \csharp{} code
% as the \emph{translation layer}
% and
%  the user-written \csharp{} service code as \emph{user code}.

%\PTComment{Cut: Figure of model.}
% \begin{figure}[thb]
% \centering
% \includegraphics[width=\linewidth]{img/fabricmodel}
% \caption{Overview of the key machines and interfaces in our Fabric model.}
% \label{fig:fabric_model}
% \end{figure}

%\PTComment{Cut: overview of model.}
% An overview of our Fabric model is shown in Figure~\ref{fig:fabric_model}.
% The \texttt{ClusterRuntime} machine 
% handles the creation and management of 
% one or more Fabric services,
% as well as service resolution requests
% which allows for client-service and inter-service communication
% within the model.
% Each Fabric service instance is managed by a \texttt{ServiceRuntime}
% machine, which in turn manages 
% several \texttt{ReplicaRuntime} machines.
% Each \texttt{ReplicaRuntime} communicates with the user code
% via several machines and interfaces from the translation layer
% (only the translation layer for the primary is shown,
% but every \texttt{ReplicaRuntime} has its own instance of the translation layer).
% Note that communication between machines is hierachical;
% thus, communication between \texttt{ReplicaRuntime}s
% (such as the sending of replication requests)
% is via the \texttt{ServiceRuntime} machine for that service.
% This approach does not necessarily reflect how Fabric works in practice.
% Instead, we chose an architecture
% that keeps the model simple
% while still allowing (what we believe to be) realistic
% asynchrony and failure scenarios.

%\PTComment{Cut: Description of how replication works in the model, including how we modeled at a fine granularity.}
% \textbf{Replication example:} In order to replicate a state-mutating operation,
% user code at the primary replica 
% calls \texttt{IStateReplicator.ReplicateAsync},
% passing the serialized operation
% object.
% The operation is sent to the \texttt{ServiceRuntime},
% where it is assigned a \emph{logical sequence number} (LSN);
% each operation is assigned a consecutive LSN
% to track the total-order in which operations should be applied.
% The LSN is sent back to the primary replica
% where it is returned from the \texttt{ReplicateAsync} call,
% along with a \texttt{Task} object that will ``complete'' once
% the operation has been replicated to a majority of
% secondaries;
% thus, the user code can wait on the \texttt{Task}
% before confirming to any clients that the request has been applied reliably.
% The \texttt{ServiceRuntime} adds the operation to its list of in-flight
% replication requests and sends $n$ events to itself to signal that the request
% must be sent to a replica, where $n$ is the number of secondary replicas.
% The reason for sending $n$ events to itself instead of simply sending events
% directly to each secondary is so that the \texttt{ServiceRuntime}
% can process a simulated failure event inbetween the sending of replica requests
% to each secondary.
% This is an example of where we carefully considered
% the granularity of actions so that we could 
% model failures appropriately.
% The user code at a secondary receives the operation,
% applies it and then calls \texttt{Acknowledge} on the operation object;
% we implement this to send an event to the \texttt{ReplicaRuntime}
% which forwards the acknowledgement to the \texttt{ServiceRuntime}.
% Once a majority of secondaries have acknowledged, the
% \texttt{ServiceRuntime} removes the replication request from its list
% of replication requests
% and sends an acknowledgement to the primary,
% where the previously returned \texttt{Task} completes.

%\PTComment{Cut: We reverse-engineered Fabric as needed.}
% \subsubsection{Fabric model correctness}
% Our model does not attempt to
% simulate the internals of Fabric accurately,
% as its purpose is to find bugs in user code
% and not in Fabric itself (which we assume to be correct).   
% However,
% due to lack of documentation,
% it is not always clear how Fabric should behave
% in certain scenarios.
% Thus,
% we ran several variants of a simple Fabric service
% that logs calls into the user code in order to
% reverse-engineer the actual behaviour of Fabric;
% we ensured that our model has the same behaviour,
% although this is an ongoing process as we encounter
% additional scenarios.

%\PTComment{Cut: We used systematic testing to find bugs in our model!}
% A further problem is that our model may contain bugs.
% In order to find bugs in our model effectively,
% we wrote a \psharp{} service made up of a single machine
% which takes the place
% of the user code and translation layer in Figure \ref{fig:fabric_model},
% for each \texttt{ReplicaRuntime}.
% Thus, we were able to run this pure \psharp{} system
% under \psharp{}'s systematic testing mode
% and uncover many assertion failures within our model.
% We tested a scenario where the primary fails at some non-deterministic point
% within the execution.

%\PTComment{Cut: Example bug found in our model plus the fix.}
% \textbf{Example Fabric model assertion failure:}
% In the buggy trace,
% the \texttt{ServiceRuntime}
% sends an \texttt{EEpochInfo} event to the second
% \texttt{ReplicaRuntime}
% indicating that this is the first epoch and the
% replica will be a secondary.
% An \emph{epoch} represents a configuration of primary and
% secondary replicas; when a different replica becomes the primary,
% this indicates the start of a new epoch.
% The \texttt{ReplicaRuntime} acknowledges that it has become
% a secondary by responding with the same event type.
% The \psharp{} service sends an \texttt{ESecondaryCopyContextOp};
% this indicates what state the secondary has
% and, thus, what the primary should send to this secondary so that it can catch
% up.
% The \texttt{ESecondaryCopyContextOp} event is forwarded to the
% \texttt{ServiceRuntime}. 
% The \texttt{ServiceRuntime} then receives and handles an \texttt{EKillPrimary}
% event, which causes the second replica to become the new primary.
% Thus,
% the \texttt{ServiceRuntime} sends another \texttt{EEpochInfo}
% to the second \texttt{ReplicaRuntime}
% indicating that this is the second epoch
% and the replica will be a primary.
% As part of this change,
% the \texttt{ReplicaRuntime}
% sends an event to the \psharp{} service
% indicating that it should stop waiting for
% the state to be copied from the old primary to this replica,
% which is acknowledged by sending an event to the \texttt{ReplicaRuntime}.
% This event causes the \texttt{ReplicaRuntime}
% to send an \texttt{ESecondaryCopyStateDone}
% event to the \texttt{ServiceRuntime},
% which unfortunately responds with an event indicating that the
% \texttt{ReplicaRuntime} is now an \emph{active} secondary
% (i.e.\ a secondary that has caught up with the primary).
% However, this causes an assertion failure because
% the \texttt{ReplicaRuntime} is becoming a primary and, thus,
% cannot be a secondary.
% Our fix to this bug was to ensure that the 
% \texttt{ESecondaryCopyStateDone} event was marked as part of the first
% epoch (as the \texttt{ReplicaRuntime} had not yet acknowledged the
% change to primary); thus, 
% the \texttt{ServiceRuntime} ignores the event and does not try to make the
% replica an active secondary.

% \subsubsection{CScale}

The main system that we tested is \emph{CScale}~\cite{faleiro2012},
a big data-stream processing system.
%In prior work~\cite{deligiannis2015psharp}, 
%we used an earlier version of the Fabric model and reported bugs in sample services.
Supporting CScale required significant additions to the model, making it much more
feature-complete.
CScale chains multiple Fabric services, which communicate via remote procedure calls (RPCs).
To close the system, we modeled RPCs 
by sending and receiving \psharp{} events.
This was enough to converted a distributed system
that uses both Fabric and its own
network communication protocol
% that runs on the Fabric platform
% and 
% uses network communication
into 
a closed single process system. 
% that uses multiple threads,
% contains
% the Fabric model
% and the CScale services,
% and does not use network communication.
%\PTComment{Cut: we had to remove static fields.}
% Additional changes were needed to
% remove certain static (per-process) fields,
% as these were inadvertently
% being shared between services
% after making the system a single process.
A key challenge in our work
was to test CScale despite the fact that it
uses various synchronous and asynchronous APIs
other than \psharp{}.
This work is still in-progress.
However, we were able to find a \texttt{NullReferenceException}
bug in CScale by running it against our Fabric model. The bug has been
communicated to the developers of CScale, but we are still awaiting a
confirmation.

>>>>

Live Table Migration (MigratingTable) is a library designed to \emph{transparently} migrate a data set between tables in an Azure Storage service \emph{while} an application is accessing this data set. This case study is particularly interesting because MigratingTable was \emph{co-developed} with its \psharp test harness. This co-development process resulted in the discovery of several tricky bugs before the system went into production (see \S\ref{sec:eval}). The MigratingTable testing effort differs from the vNext case study: the vNext developers focused on a single liveness property, while the MigratingTable test harness checks complete compliance with an interface (safety) specification.

MigratingTable provides a \emph{virtual table} that has an interface similar to an ordinary Azure table. This interface is named \texttt{IChainTable}. A virtual table is backed by a pair of \emph{old} and \emph{new} \emph{backend} tables, both of which implement \texttt{IChainTable}. A \emph{migrator} job is responsible for moving all data from the old table to the new table in the background. Meanwhile, each read and write operation issued to the virtual table is translated to a sequence of reads and writes on the backend tables according to a protocol, which intends to guarantee that when multiple applications issue \emph{input} operations to virtual tables that are backed by the same backend tables, the output is compliant with the specification of \texttt{IChainTable} for the combined \emph{input history} as if all the operations were done on a single table. The goal of using \psharp was to systematically test this property.

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{img/modeled_migration}
\caption{The \psharp test harness of MigratingTable (each box with a dotted line represents one \psharp machine).}
\label{fig:mockedmigration}
\end{figure}

@@

The developers instrumented MigratingTable to report the intended \emph{linearization point} of each input operation on its corresponding virtual table. This allows the \psharp test harness to keep \texttt{SpecTable} in sync with the virtual table: the \texttt{Service} machine sends each input operation to \texttt{SpecTable} when the linearization point on the virtual table is reached. The output of the operation on the virtual table is then checked against its output on \texttt{SpecTable}.

@@

\psharp captures and controls all the interleaving in the system, and systematically explores them. To ensure that \texttt{SpecTable} is never observed to be out of sync with the backend tables, which could lead to false positives, after the \texttt{Tables} machine processes a backend operation, it enters a state that defers further backend operations until MigratingTable has reported whether the backend operation was a linearization point and (if so) the operation on \texttt{SpecTable} has been completed.

@@
